Predicting trends in the quality of state-of-the-art neural networks without access to training or testing data

### 2020-10-01 submission/NatCom_cv_models.tex
pass to address most of the presubmission comments for nat comm

    \subfigure[ ResNet, Log $\alpha$-Norm ]{
        \includegraphics[width=4.9cm]{img/ResNet_logpnorm_accs.png}
        \label{fig:resnet-accuracy}
    }
    \qquad
    \subfigure[ ResNet-1K, Log $\alpha$-Norm ]{
        \includegraphics[width=4.9cm]{img/ResNet-1K_logpnorm_accs.png}
        \label{fig:resnet1k-accuracy}
    }
    \caption{Comparison of Average $\alpha$-Norm quality metric ($\langle\log\Vert\mathbf{X}\Vert_{\alpha}^{\alpha}\rangle$) versus reported Top1 test accuracy for the ResNet and ResNet-1K pretrained (pyTorch) models. }
    \label{fig:cv2-accuracy}
\end{figure}

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|p{1in}|c|c|c|c|c|}
\hline
 Series    &\#   & $\langle\log\Vert\mathbf{W}\Vert_{F}\rangle$ & $\langle\log\Vert\mathbf{W}\Vert_{\infty}\rangle$ & $\hat{\alpha}$ & $\langle\log\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}\rangle$ \\
\hline
 VGG       &  6 & 0.56 & 0.53 & 0.48          & \textbf{0.42}  \\
 ResNet    &  5 & 0.9  & 1.4  & \textbf{0.61} & 0.66           \\
 ResNet-1K & 19 & 2.4  & 3.6  & \textbf{1.8}  & 1.9            \\
 DenseNet  &  4 & 0.3  & 0.26 & \textbf{0.16} & 0.21           \\
\hline
\end{tabular}
\end{center}
\caption{RMSE (smaller is better) for linear fits of 
         quality metrics to reported Top1 test error for pretrained models in each architecture series.  Column \# refers to number of models.  VGG, ResNet, and DenseNet were pretrained on ImageNet, and ResNet-1K was pretrained on ImageNet-1K. 
}
\label{table:cv-models}
\end{table}

@@

\paragraph{Variation in Data Set Size.}

@@

\paragraph{Comparison of VGG, ResNet, and DenseNet Architectures.}

These layer-wise observations can be understood in terms of architectural differences between VGG, ResNet, and DenseNet.
VGG resembles the traditional convolutional architectures, such as LeNet5, and consists of several [Conv2D-Maxpool-ReLu] blocks, followed by 3 large Fully Connected (FC) layers.
ResNet greatly improved on VGG by replacing the large FC layers, shrinking the Conv2D blocks, and introducing residual connections.
This optimized approach allows for greater accuracy with far fewer parameters, and ResNet models of up to 1000 layers have been trained~\cite{resnet1000}.

The efficiency and effectiveness of ResNet seems to be reflected in the smaller and more stable $\alpha\sim 2.0$, across nearly all layers, indicating that the inner layers are very well correlated and more strongly optimized.
This contrasts with the DenseNet models, which contains many connections between every layer.
These results (large $\alpha$, meaning that even a PL model is probably a poor fit) suggest that DenseNet has too many connections, diluting high quality interactions across layers, and leaving many layers very poorly~optimized.

Fine-scale measurements such as these enable us to form hypotheses as to the inner workings of DNN models, opening the door to an improved understanding of \emph{why} DNNs work, as well as \emph{how} to design better DNN models.
We next turn to two such~examples.

\paragraph{Correlation Flow.}

Figure~\ref{fig:3models-alpha-layers} can be understood in terms of what we will call \emph{Correlation Flow}.
The average Log $\alpha$-Norm metric and the Weighted Alpha metric are based on HT-SR Theory~\cite{MM18_TR, MM19_HTSR_ICML, MM20_SDM}, which is in turn based on the statistical mechanics of heavy tailed and strongly correlated systems~\cite{BouchaudPotters03, SornetteBook, BP11, bun2017}. 
There, one expects that the weight matrices of well-trained DNNs will exhibit correlations over many size scales, as is well-known in other strongly-correlated systems~\cite{BouchaudPotters03, SornetteBook}. 
This would imply that their ESDs can be well-fit by a truncated PL, with exponents $\alpha\in[2,4]$.
Much larger values $(\alpha\gg 6)$ may reflect poorer PL fits, whereas smaller values $(\alpha\sim 2)$, are associated with models that generalize better.

@@

The similarity between norm-based metrics and PL-based metrics suggests a question: Is the Weighted Alpha metric just a variation of more familiar norm-based metrics?  
More generally, do fitted $\alpha$ values contain information not captured by norms? 
Among hundreds of pretrained models, there are ``exceptions that prove the rule.'' 
To show that $\alpha$ does capture something different, we show that some compression/distillation methods \cite{CWZZ17_TR} may actually damage models unexpectedly, by introducing what we call \emph{Scale Collapse}, where several distilled layers have unexpectedly small Spectral Norms.

@@

Pretrained models in the \texttt{distiller} package have passed some quality metric, but they are much less well trodden than any of the VGG, ResNet, or DenseNet series.  
The obvious interpretation is that, while norms make good regularizers for a single model, there is no reason \emph{a priori} to expect them correlate well with test accuracies across different models, and they may not differentiate well-trained versus poorly-trained models.
We do expect, however, the PL $\alpha$ to do so, because it effectively measures the amount of information correlation in the model~\cite{MM18_TR, MM19_HTSR_ICML, MM20_SDM}.
This suggests that the $\alpha$ values will improve, i.e., decrease, over time, as distillation techniques continue to improve.
The reason for the anomalous behavior shown in 
Figure~\ref{fig:resnet204D5L}
is that the \texttt{distiller} Group Regularization technique 
causes the norms of the $\mathbf{W}$ pre-activation maps for two Conv2D layers to increase spuriously.
This is difficult to diagnose by analyzing training/test curves, but it is easy to diagnose with our~approach.

>>>>

    \subfigure[ ResNet, Log $\alpha$-Norm ]{
        \includegraphics[width=4.9cm]{img/ResNet_logpnorm_accs.png}
        \label{fig:resnet-accuracy}
    }
    \qquad
    \subfigure[ ResNet-1K, Log $\alpha$-Norm ]{
        \includegraphics[width=4.9cm]{img/ResNet-1K_logpnorm_accs.png}
        \label{fig:resnet1k-accuracy}
    }
    \caption{Comparison of Average $\alpha$-Norm quality metric versus reported Top1 test accuracy for the ResNet and ResNet-1K pretrained (pyTorch) models. 
             \michael{Symbols and text are way to small on these and other figures; axes/ticks way too small; need different symbols, not just red versus green; etc.}
            }
    \label{fig:cv2-accuracy}
\end{figure}

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|p{1in}|c|c|c|c|c|}
\hline
 Series    &\#   & $\langle\log\Vert\mathbf{W}\Vert_{F}\rangle$ & $\langle\log\Vert\mathbf{W}\Vert_{\infty}\rangle$ & $\hat{\alpha}$ & $\langle\log\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}\rangle$ \\
\hline
 VGG       &  6 & 0.56 & 0.53 & 0.48          & \textbf{0.42}  \\
 ResNet    &  5 & 0.9  & 1.4  & \textbf{0.61} & 0.66           \\
 ResNet-1K & 19 & 2.4  & 3.6  & \textbf{1.8}  & 1.9            \\
 DenseNet  &  4 & 0.3  & 0.26 & \textbf{0.16} & 0.21           \\
\hline
\end{tabular}
\end{center}
\caption{RMSE (smaller is better) for linear fits of 
         quality metrics to reported Top1 test error for pretrained models in each architecture series.  
         Column \# refers to number of models.  
         VGG, ResNet, and DenseNet were pretrained on ImageNet.  
         ResNet-1K was pretrained on ImageNet-1K. 
}
\label{table:cv-models}
\end{table}

@@

@@

\paragraph{Correlation Flow; or How $\alpha$ Varies Across Layers.}

Figure~\ref{fig:3models-alpha-layers} can be understood in terms of what we will call Correlation Flow.
The average Log $\alpha$-Norm metric and the Weighted Alpha metric are based on HT-SR Theory~\cite{MM18_TR, MM19_HTSR_ICML, MM20_SDM}, which is in turn based on the statistical mechanics of heavy tailed and strongly correlated systems~\cite{BouchaudPotters03, SornetteBook, BP11, bun2017}. 
There, one expects that the weight matrices of well-trained DNNs will exhibit correlations over many size scales, as is well-known in other strongly-correlated systems~\cite{BouchaudPotters03, SornetteBook}. 
This would imply that their ESDs can be well-fit by a truncated PL, with exponents $\alpha\in[2,4]$.
Much larger values $(\alpha\gg 6)$ may reflect poorer PL fits, whereas smaller values $(\alpha\sim 2)$, are associated with models that generalize better.

@@

The similarity between norm-based metrics and PL-based metrics may lead one to wonder whether the Weighted Alpha metric is just a variation of more familiar norm-based metrics.  
Among hundreds of pretrained models, there are ``exceptions that prove the rule,'' and these can be used to show that fitted $\alpha$ values do contain information not captured by norms. 
To illustrate this, we show that some compression/distillation methods \cite{CWZZ17_TR} may actually damage models unexpectedly, by introducing what we call Scale Collapse, where several distilled layers have unexpectedly small Spectral Norms.

@@

Pretrained models in the \texttt{distiller} package have passed some quality metric, but they are much less well trodden than any of the VGG, ResNet, or DenseNet series.  
The obvious interpretation is that, while norms make good regularizers for a single model, there is no reason a priori to expect them correlate well with test accuracies across different models, and they may not differentiate well-trained versus poorly-trained models.
We do expect, however, the PL $\alpha$ to do so, because it effectively measures the amount of information correlation in the model~\cite{MM18_TR, MM19_HTSR_ICML, MM20_SDM}.
This suggests that the $\alpha$ values will improve, i.e., decrease, over time, as distillation techniques continue to improve.
The reason for the anomalous behavior shown in 
Figure~\ref{fig:resnet204D5L}
is that the \texttt{distiller} Group Regularization technique 
causes the norms of the $\mathbf{W}$ pre-activation maps for two Conv2D layers to increase spuriously.
This is difficult to diagnose by analyzing training/test curves, but it is easy to diagnose with our~approach.

### 2020-10-01 submission/NatCom_discussion.tex
pass to address most of the presubmission comments for nat comm

@@

We have developed and evaluated methods to predict trends in the quality of state-of-the-art neural networks---without access to training or testing data.
Our main methodology involved weight matrix meta-analysis, using the publicly-available \emph{WeightWatcher} tool~\cite{weightwatcher_package}, and informed by the recently-developed HT-SR Theory~\cite{MM18_TR, MM19_HTSR_ICML, MM20_SDM}.
Prior to our work, it was not even obvious that norm-based metrics would perform well to predict trends in quality \emph{across} models (as they are usually used \emph{within} a given model or parameterized model class, e.g., to bound generalization error or to construct regularizers).
Our results are the first to demonstrate that they can be used for this important practical problem.
%
Our results also demonstrate that PL-based metrics perform better than norm-based metrics. 
This should \emph{not} be surprising---at least to those familiar with the statistical mechanics of heavy tailed and strongly correlated systems~\cite{BouchaudPotters03, SornetteBook, BP11, bun2017}---since our use of PL exponents is designed to capture the idea that well-trained models capture information correlations over many size scales in the data.
Again, though, our results are the first to demonstrate this.
%
Our approach can also be used to provide fine-scale insight (rationalizing the flow of correlations or the collapse of size scale) throughout a network. 
Both \emph{Correlation Flow} and \emph{Scale Collapse} are important for improved diagnostics on pretrained models as well as for improved training methodologies.

Statistical mechanics has long had influence on DNN theory and practice~\cite{EB01_BOOK, MM17_TR, BKPx20}.
Our best-performing PL-based metrics are based on statistical mechanics via HT-SR Theory~\cite{MM17_TR, MM18_TR, MM19_HTSR_ICML, MM19_KDD, MM20_SDM}.
The way in which we (and HT-SR Theory) \emph{use} statistical mechanics theory is quite different than the way it is more commonly formulated~\cite{EB01_BOOK, BKPx20}.
Going beyond idealized models, we \emph{use} statistical mechanics in a broader sense, drawing upon techniques from quantitative finance, random matrix theory, and the statistical mechanics of heavy tailed and strongly correlated systems~\cite{BouchaudPotters03, SornetteBook, BP11, bun2017}.
%
There is also a large body of work in ML on using norm-based metrics to bound generalization error~\cite{NTS15, BFT17_TR, LMBx18_TR}.
This theoretical work aims to prove generalization bounds, and this applied work then uses these norms to construct regularizers to improve training.
Proving generalization bounds and developing new regularizers is very different than our focus of validating pretrained models.

Our work, starting in 2018 with the \emph{WeightWatcher} tool~\cite{weightwatcher_package}, is the first to perform a detailed analysis of the weight matrices of DNNs~\cite{MM18_TR, MM19_HTSR_ICML, MM20_SDM}.
Subsequent to the initial version of this paper, we became aware of two other works that were posted to the in 2020 within weeks of the initial version of this paper~\cite{EJRUY20_TR,UKGBT20_TR}.
Both of these papers validate our basic result that one can gain substantial insight into model quality by examining weight matrices without access to any training or testing data.
However, both consider smaller models drawn from a much narrower range of applications than we consider.
Previous results in HT-SR Theory suggest that insights from these smaller models may not extend to the state-of-the-art CV and NLP models we consider.

@@

We conclude with a few comments on what a \emph{practical theory} of DNNs should look like.
To do so, we distinguish between two types of theories:
\emph{non-empirical or analogical theories}, in which one creates, often from general principles, a very simple toy model that can be analyzed rigorously, and one then argues that the model is relevant to the system of interest; and 
\emph{semi-empirical theories}, in which there exists a rigorous asymptotic theory, which comes with parameters, for the system of interest, and one then adjusts or fits those parameters to the finite non-asymptotic data.
A drawback of the former approach is that it typically makes very strong assumptions, and the strength of those assumptions can limit the practical applicability of the theory.
Nearly all of the work on DNN theory focuses on the former type of theory.
Our approach focuses on the latter type of theory.
Our results, which are based on \emph{using} sophisticated statistical mechanics theory and \emph{solving} important practical DNN problems, suggests that the latter approach should be of interest more generally for those interested in developing a \emph{practical DNN~theory}.

>>>>

\paragraph{Comparison of VGG, ResNet, and DenseNet Architectures.}

Going beyond the goal of predicting trends in the quality of state-of-the-art neural networks without access to training or testing data, observations such as
the layer-wise observations we described in Figure~\ref{fig:3models-alpha-layers} can be understood in terms of architectural differences between VGG, ResNet, and DenseNet.
VGG resembles the traditional convolutional architectures, such as LeNet5, and consists of several [Conv2D-Maxpool-ReLu] blocks, followed by 3 large Fully Connected (FC) layers.
ResNet greatly improved on VGG by replacing the large FC layers, shrinking the Conv2D blocks, and introducing residual connections.
This optimized approach allows for greater accuracy with far fewer parameters, and ResNet models of up to 1000 layers have been trained~\cite{resnet1000}.

The efficiency and effectiveness of ResNet seems to be reflected in the smaller and more stable $\alpha\sim 2.0$, across nearly all layers, indicating that the inner layers are very well correlated and more strongly optimized.
This contrasts with the DenseNet models, which contains many connections between every layer.
These results (large $\alpha$, meaning that even a PL model is probably a poor fit) suggest that DenseNet has too many connections, diluting high quality interactions across layers, and leaving many layers very poorly~optimized.
%
Fine-scale measurements such as these enable us to form hypotheses as to the inner workings of DNN models, opening the door to an improved understanding of why DNNs work, as well as how to design better DNN models.
Correlation Flow and Scale Collapse are two such~examples.

Statistical mechanics has long had influence on DNN theory and practice~\cite{EB01_BOOK, MM17_TR, BKPx20}.
Our best-performing PL-based metrics are based on statistical mechanics via HT-SR Theory~\cite{MM17_TR, MM18_TR, MM19_HTSR_ICML, MM19_KDD, MM20_SDM}.
The way in which we (and HT-SR Theory) use statistical mechanics theory is quite different than the way it is more commonly formulated~\cite{EB01_BOOK, BKPx20}.
Going beyond idealized models, we use statistical mechanics in a broader sense, drawing upon techniques from quantitative finance, random matrix theory, and the statistical mechanics of heavy tailed and strongly correlated systems~\cite{BouchaudPotters03, SornetteBook, BP11, bun2017}.
There is also a large body of work in ML on using norm-based metrics to bound generalization error~\cite{NTS15, BFT17_TR, LMBx18_TR}.
This theoretical work aims to prove generalization bounds, and this applied work then uses these norms to construct regularizers to improve training.
Proving generalization bounds and developing new regularizers is very different than our focus of validating pretrained models.

Our work, starting in 2018 with the \texttt{WeightWatcher} tool~\cite{weightwatcher_package}, is the first to perform a detailed analysis of the weight matrices of DNNs~\cite{MM18_TR, MM19_HTSR_ICML, MM20_SDM}.
Subsequent to the initial version of this paper, we became aware of two other works that were posted to the in 2020 within weeks of the initial version of this paper~\cite{EJRUY20_TR,UKGBT20_TR}.
Both of these papers validate our basic result that one can gain substantial insight into model quality by examining weight matrices without access to any training or testing data.
However, both consider smaller models drawn from a much narrower range of applications than we consider.
Previous results in HT-SR Theory suggest that insights from these smaller models may not extend to the state-of-the-art CV and NLP models we consider.

@@

We have developed and evaluated methods to predict trends in the quality of state-of-the-art neural networks---without access to training or testing data.
Our main methodology involved weight matrix meta-analysis, using the publicly-available \texttt{WeightWatcher} tool~\cite{weightwatcher_package}, and informed by the recently-developed HT-SR Theory~\cite{MM18_TR, MM19_HTSR_ICML, MM20_SDM}.
Prior to our work, it was not even obvious that norm-based metrics would perform well to predict trends in quality across models (as they are usually used within a given model or parameterized model class, e.g., to bound generalization error or to construct regularizers).
Our results are the first to demonstrate that they can be used for this important practical problem.
Our results also demonstrate that PL-based metrics perform better than norm-based metrics. 
This should not be surprising---at least to those familiar with the statistical mechanics of heavy tailed and strongly correlated systems~\cite{BouchaudPotters03, SornetteBook, BP11, bun2017}---since our use of PL exponents is designed to capture the idea that well-trained models capture information correlations over many size scales in the data.
Again, though, our results are the first to demonstrate this.
Our approach can also be used to provide fine-scale insight (rationalizing the flow of correlations or the collapse of size scale) throughout a network. 
Both Correlation Flow and Scale Collapse are important for improved diagnostics on pretrained models as well as for improved training methodologies.

@@

More generally, our results suggest what a practical theory of DNNs should look like.
To see this, let's distinguish between two types of theories:
non-empirical or analogical theories, in which one creates, often from general principles, a very simple toy model that can be analyzed rigorously, and one then claims that the model is relevant to the system of interest; and 
semi-empirical theories, in which there exists a rigorous asymptotic theory, which comes with parameters, for the system of interest, and one then adjusts or fits those parameters to the finite non-asymptotic data, to make predictions about practical problems.
A drawback of the former approach is that it typically makes very strong assumptions, and the strength of those assumptions can limit the practical applicability of the theory.
Nearly all of the work on DNN theory focuses on the former type of theory.
Our approach focuses on the latter type of theory.
Our results, which are based on using sophisticated statistical mechanics theory and solving important practical DNN problems, suggests that the latter approach should be of interest more generally for those interested in developing a practical DNN~theory.

### 2020-10-01 submission/NatCom_introduction.tex
pass to address most of the presubmission comments for nat comm

Most importantly, in industry, one faces unique practical problems such as: do we have enough data for this model? 
Indeed, high quality, labeled data can be very expensive to acquire, and this cost can make or break a project.
Methods that are developed and evaluated on any well-defined publicly-available corpus of data, no matter how large or diverse or interesting, are clearly not going to be well-suited to address problems such as this.
It is of great practical interest to have metrics to evaluate the quality of a trained model---in the absence of training/testing data and without any detailed knowledge of the training/testing process.  
There is a need for a practical theory for pretrained models which can predict how, when, and why such models can be expected to perform well or~poorly.

In the absence of training and testing data, obvious quantities to examine are the weight matrices of pretrained models, e.g., 
properties such as norms of weight matrices and/or parameters of Power Law (PL) fits of the eigenvalues of weight matrices.
Norm-based metrics have been used in traditional statistical learning theory to bound capacity and construct regularizers; and PL fits are based on statistical mechanics approaches to deep neural networks (DNNs).
While we use traditional norm-based and PL-based metrics, our goals are not the traditional goals.
Unlike more common ML approaches, we do not seek a bound on the generalization (e.g., by evaluating training/test errors), we do not seek a new regularizer, and we do not aim to evaluate a single model (e.g., as with hyperparameter optimization).
Instead, we want to examine different models across common architecture series, and we want to compare models between different architectures themselves.
In both cases, we ask:
Can we predict trends in the quality of pretrained DNN models without access to training or testing data?

To answer this question, we provide a detailed empirical analysis, evaluating quality metrics for pretrained DNN models, and we do so at scale.
Our approach may be viewed as a statistical meta-analysis of previously published work, where we consider a large suite of hundreds of publicly-available models, mostly from computer vision (CV) and natural language processing (NLP).
By now, there are many such state-of-the-art models that are publicly-available, e.g., 
hundreds of pretrained models in CV ($\ge 500$) and NLP ($\approx 100$).%
\footnote{When we began this work in 2018, there were fewer than tens of such models; now in 2020, there are hundreds of such models; and we expect that in a year or two there will be an order of magnitude or more of such models.}
For all these models, we have no access to training data or testing data, and we have no specific knowledge of the training/testing protocols. 
%
Here is a summary of our main results.
First, norm-based metrics do a reasonably good job at predicting quality trends in well-trained CV/NLP models.
Second, norm-based metrics may give spurious results when applied to poorly-trained models (e.g., models trained without enough data, etc.).
For example, they may exhibit what we call \emph{Scale Collapse} for these models. 
Third, PL-based metrics do much better at predicting quality trends in pretrained CV/NLP models.  
They are qualitatively better at discriminating well-trained versus poorly-trained models, and quantitatively better at discriminating among a series of well-trained versus very-well-trained models.
Fourth, PL-based metrics can also be used to characterize fine-scale model properties, including what we call layer-wise \emph{Correlation Flow}, in well-trained and poorly-trained models; and they can be used to evaluate model enhancements (e.g., distillation, fine-tuning, etc.).
%
Our work provides a theoretically-principled empirical evaluation---by far the largest, most detailed, and most comprehensive to date---and the theory we apply was developed previously~\cite{MM18_TR, MM19_HTSR_ICML, MM20_SDM}.
Performing such a meta-analysis of previously-published work is common in certain areas, but it is quite rare in ML, where the emphasis is on developing better training protocols.

>>>>

Most importantly, in industry, one faces unique practical problems such as determining whether one has enough data for a given model. 
Indeed, high quality, labeled data can be very expensive to acquire, and this cost can make or break a project.
Methods that are developed and evaluated on any well-defined publicly-available corpus of data, no matter how large or diverse or interesting, are clearly not going to be well-suited to address problems such as this.
It is of great practical interest to have metrics to evaluate the quality of a trained model---in the absence of training/testing data and without any detailed knowledge of the training/testing process.  
There is a need for a practical theory for pretrained models which can predict how, when, and why such models can be expected to perform well or~poorly.

In the absence of training and testing data, obvious quantities to examine are the weight matrices of pretrained models, e.g., 
properties such as norms of weight matrices and/or parameters of Power Law (PL) fits of the eigenvalues of weight matrices.
Norm-based metrics have been used in traditional statistical learning theory to bound capacity and construct regularizers; and PL fits are based on statistical mechanics approaches to deep neural networks (DNNs).
While we use traditional norm-based and PL-based metrics, our goals are not the traditional goals.
Unlike more common ML approaches, we do not seek a bound on the generalization (e.g., by evaluating training/test errors), we do not seek a new regularizer, and we do not aim to evaluate a single model (e.g., as with hyperparameter optimization).
Instead, we want to examine different models across common architecture series, and we want to compare models between different architectures themselves.
In both cases, one can ask whether it is possible to predict trends in the quality of pretrained DNN models without access to training or testing data.

To answer this question, we provide a detailed empirical analysis, evaluating quality metrics for pretrained DNN models, and we do so at scale.
Our approach may be viewed as a statistical meta-analysis of previously published work, where we consider a large suite of hundreds of publicly-available models, mostly from computer vision (CV) and natural language processing (NLP).
By now, there are many such state-of-the-art models that are publicly-available, e.g., 
hundreds of pretrained models in CV ($\ge 500$) and NLP ($\approx 100$).%
\footnote{When we began this work in 2018, there were fewer than tens of such models; now in 2020, there are hundreds of such models; and we expect that in a year or two there will be an order of magnitude or more of such models.}
For all these models, we have no access to training data or testing data, and we have no specific knowledge of the training/testing protocols. 
%
Here is a summary of our main results.
First, norm-based metrics do a reasonably good job at predicting quality trends in well-trained CV/NLP models.
Second, norm-based metrics may give spurious results when applied to poorly-trained models (e.g., models trained without enough data, etc.).
For example, they may exhibit what we call Scale Collapse for these models. 
Third, PL-based metrics do much better at predicting quality trends in pretrained CV/NLP models.  
They are qualitatively better at discriminating well-trained versus poorly-trained models, and quantitatively better at discriminating among a series of well-trained versus very-well-trained models.
Fourth, PL-based metrics can also be used to characterize fine-scale model properties, including what we call layer-wise Correlation Flow, in well-trained and poorly-trained models; and they can be used to evaluate model enhancements (e.g., distillation, fine-tuning, etc.).
%
Our work provides a theoretically-principled empirical evaluation---by far the largest, most detailed, and most comprehensive to date---and the theory we apply was developed previously~\cite{MM18_TR, MM19_HTSR_ICML, MM20_SDM}.
Performing such a meta-analysis of previously-published work is common in certain areas, but it is quite rare in ML, where the emphasis is on developing better training protocols.
